### 2018-04-25 Physics Notes/Turning Points/Overall Notes/Turning Points.tex
Notes Update

\section{Microscopes}

@@

\subsection{Transmission electron microscope}

@@

\subsection{Scanning Tunnelling Microscope}
\includegraphics[width=6cm]{stm.png}
This has a very fine conducting probe very close to the surface of the sample.

>>>>

\subsection{Microscopes}

@@

\subsubsection{Transmission electron microscope}

@@

\subsubsection{Scanning Tunnelling Microscope}
\includegraphics[width=6cm]{stm.png}\\
This has a very fine conducting probe very close to the surface of the sample. Quantum tunnelling means that over the very short distance there is a small probability electrons will cross the gap. A small voltage is maintained between the tip of the probe and the sample to ensure the electrons travel the right way.\\
An STM can either have the probe at a constant height, and measure the current, or alter the height to keep constant current, and measure the height.
\subsection{Newton's CT of light}
Definition - Light is made up of tiny particles called corpuscles that always travel in a straight line
\subsubsection{Reflection and refraction}
Newton believed this theory was true as it can explain both reflection and refraction\\
\includegraphics[width=6cm]{reflection.png}
\includegraphics[width=6cm]{refraction.png}\\
\textbf{Reflection} - These corpuscles have perfectly elastic collisions, meaning that the speed before is the speed after. The horizontal velocity doesn't change, the vertical velocity is inverted. Therefore angle of incidence equals angle of reflection.\\
\textbf{Refraction} - Newton said the corpuscles were attracted into the material, causing them to travel faster, causing the component of the velocity perpendicular to the boundary to increase, causing angle with the normal to reduce. Newton was wrong.
\subsubsection{Rival theories}
Christiaan Huygens proposed the wave front theory, which is the theory we have been taught to describe refraction and diffraction. This described light travelling slower in a more dense material.\\
Why Huygens' theory was rejected:
\item It was not possible to measure the speed of light at that scale at that time, meaning neither theory could be proved correct or incorrect.
\item Newton had a better reputation
\item The wave theory only considered longitudinal waves so couldn't explain polarisation.
\subsection{The Discovery of photoelectricity}
Black body - A theoretical perfect absorber and emitter of radiation\\
Ultraviolet catastrophe - Where short wavelength radiation is incident on a black body, causing it to emit an infinite amount of power per unit wavelength
\subsubsection{The failure of classical wave theory to explain observations on photoelectricity}
\item Wave theory suggested that given enough time, electrons would gain enough energy from a wave to escape
\item There would be a time lag between the light being incident and the emission of an electron
\item Any frequency would be able to cause electron emission given enough time
\subsubsection{Einstein's Explanation of photoelectricity}
Einstein showed electrons must have energy greater than the work function in order to escape a metal. Kinetic energy is the energy difference between the energy of the electron and the work function.
\subsection{The significance of Young's double slit experiment}
Young's double slit experiment showed interference, disproving Newton's Corpuscular Theory, however Huygen's wave theory was not accepted until Fizeau compared the speed of light in water and air.
\subsection{Wave particle duality}
By using the equations
$$\frac{1}{2}mv^2=eV \ \textrm{and} \ \lambda=\frac{h}{mv}$$
They can be used to get the equation
$$\lambda=\frac{h}{\sqrt{2meV}}$$
